SDR enhancement by clouds

### 2024-03-26 article/article.Rmd
Commit 2024-03-26 20:14

The underling mechanism of those events have been studied, with the main factor to be
.... cite ...
The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances [@Yordanov2015].

>>>>

There are some propositions of the underling mechanism of those events as summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].
The overall phenomenon can depend on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the observer.
As such, th

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances [@Yordanov2015].

### 2024-03-26 article/article.tex
Commit 2024-03-26 20:14

The underling mechanism of those events have been studied, with the main factor to be
\ldots. cite \ldots{}
The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances (Yordanov, Saetre, and Midtgård 2015).

>>>>

There are some propositions of the underling mechanism of those events as summarized
by (\textbf{Gueymard2017?}), and include scattering on the edge of cumulus clouds or through
thin cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
(\textbf{Pecenak2016?}; \textbf{Thuillier2013?}; \textbf{Yordanov2013?}; Yordanov, Saetre, and Midtgård 2015).
The overall phenomenon can depend on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the observer.
As such, th

The forward scattering of clouds near the sun has been observed to produce cases of
extreme enhancement irradiances (Yordanov, Saetre, and Midtgård 2015).
